\Large{Learning to Pivot with Adversarial Networks}

### 2016-10-30 tex/paper.tex
one more step of cleanup
updated intro

\newcommand{\glnote}[1]{\textcolor{red}{[GL: #1]}}

@@

\title{\Large{Adversarial Training against Systematic Uncertainty}}
\vspace{1cm}
\author{\small{\bf Gilles Louppe}\thanks{\texttt{g.louppe@nyu.edu}}}
\affiliation{New York University}
\author{\small{\bf Michael Kagan}\thanks{\texttt{makagan@slac.stanford.edu}}}
\affiliation{SLAC National Accelerator Laboratory}
\author{\small{\bf Kyle Cranmer}\thanks{\texttt{kyle.cranmer@nyu.edu}}}
\affiliation{New York University}

@@

@@

Our goal
is to learn a score function $f(\cdot;\theta_f) : \mathbb{R}^p \mapsto {\cal S}$ of
parameters $\theta_f$ (e.g., a neural network-based probabilistic classifier) and minimizing  a loss ${\cal L}_f(\theta_f)$ (e.g.,
the cross-entropy). In addition, we require that the distribution of $f(X_z ; \theta_f)$ should be
robust to the value $z$ of the nuisance parameter  -- which remains unknown at
test time.

We propose  to
solve the  problem of finding a predictive function $f$ such that
\begin{equation}\label{eqn:criterion}
    p(f(X ; \theta_f) = s | z ) = p(f(X ; \theta_f) = s | z^\prime )
\end{equation}
for all $z,z^\prime \in  {\cal Z}$ and all values $s \in {\cal S}$ of $f(X ; \theta_f)$.
In words, we are looking for a predictive function $f$
which is a pivotal quantity \citep{degroot1986probability} with respect to the
nuisance parameter. That is, such that  the distribution of $f(X_z; \theta_f)$
is invariant with respect to the value $z$ of the nuisance.

@@

\glnote{Add paper outline.}

@@

\subsection{High energy physics example}

@@

\section{Related work}

@@

\section{Conclusions}

>>>>

\newcommand{\glnote}[1]{\textcolor{red}{[GL: #1]}}
\newcommand{\kcnote}[1]{\textcolor{red}{[KC: #1]}}

@@

\title{\Large{Learning to Pivot with Adversarial Networks}}
\vspace{1cm}
\author{\small{\bf Gilles Louppe}\thanks{\texttt{g.louppe@nyu.edu}}}
\affiliation{New York University}
\author{\small{\bf Michael Kagan}\thanks{\texttt{makagan@slac.stanford.edu}}}
\affiliation{SLAC National Accelerator Laboratory}
\author{\small{\bf Kyle Cranmer}\thanks{\texttt{kyle.cranmer@nyu.edu}}}
\affiliation{New York University}

@@

Machine learning techniques have been used to enhance a number of scientific disciplines, 
and they have the potential to transform even more of the scientific process.
One of the challenges of applying machine learning techniques to scientific 
problems is the need to incorporate systematic uncertainties. The presence of systematic
uncertainties affects both the robustness of inference and the metrics used to evaluate the 
performance of a particular data analysis strategy.

We will focus on supervised learning techniques where the presence of systematic 
uncertainty can be associated to the fact that the data generation process is not uniquely 
specified. In other words, the lack of systematic uncertainties corresponds to the case 
that the process that generates training data is unique, fully specified, 
and an accurate representative of the real world data.

A common situation when systematic uncertainty is present is when the training data are not representative of
the real data that a predictive model will be applied to in practice. Several techniques for domain adaptation have
been developed to create predictive models that are more robust to this type of uncertainty.

Another common situation is that there are several plausible data generation processes. We consider the situation of a 
family of data generation processes parametrized by nuisance parameters, which can be categorical or continuous. In particular, we consider the probability model $p(X,Y,Z)$, where $X$ are the data, $Y$ are the target labels, and $Z$ are the nuisance parameters. We will consider the problem of learning a predictive model for $Y$ conditional on the observed values of $X$ that is robust to uncertainty in the unknown value of $Z$.

\kcnote{Fill in outline}

In Sec.~\ref{sec:problem}  Sec.~\ref{sec:method}  Sec.~\ref{sec:theory}  Sec.~\ref{sec:toy}  Sec.~\ref{sec:hep} 
 Sec.~\ref{sec:related}  Sec.~\ref{sec:conclusions} .

@@

We begin with a family of data generation processes $p(X,Y,Z)$, where $X$ are the data, $Y$ are the target labels, and $Z$ are the nuisance parameters that can be continuous or categorical. We can use this model to generate training data for $X$ conditional on both $Y$ and $Z$. Our goal is to learn a predictive model $f(\cdot;\theta_f) : \mathbb{R}^p \mapsto {\cal S}$ of
parameters $\theta_f$ (e.g., a neural network-based probabilistic classifier) and minimizing  a loss ${\cal L}_f(\theta_f)$ (e.g.,
the cross-entropy).

In addition, we would like that inference based on $f(X ; \theta_f)$ should be
robust to the value $z$ of the nuisance parameter  -- which remains unknown at
test time. A formal way of enforcing robustness is to require that the distribution of 
$f(X ; \theta_f)$ conditional on $Z$ (and possibly $Y$) be invariant to the value $Z$
 of the nuisance parameter. Thus, we wish find a predictive function $f$ such that
\begin{equation}\label{eqn:criterion}
    p(f(X ; \theta_f) = s | z ) = p(f(X ; \theta_f) = s | z^\prime )
\end{equation}
for all $z,z^\prime \in  {\cal Z}$ and all values $s \in {\cal S}$ of $f(X ; \theta_f)$.
In words, we are looking for a predictive function $f$
which is a pivotal quantity \citep{degroot1986probability} with respect to the
nuisance parameter. That is, such that  the distribution of $f(X_z; \theta_f)$
is invariant with respect to the value $z$ of the nuisance.

\kcnote{adjust text for conditional on Y as well}

@@

@@

\subsection{High energy physics example}
\label{sec:hep}

@@

\section{Related work}
\label{sec:related}

@@

\section{Conclusions}
\label{sec:conclusions}
